Fractional Types

### 2019-11-21 fracGC/p.tex
subtitle
plan for space section

\title{Fractional Types}
\author{Chao-Hong Chen}
\affiliation{
  \institution{Indiana University}
}

@@

cardinality of pi type:
\PIMEMcard{}

enumeration:
\PIMEMenum{}

combinator preserve size:
\PIMEMcardeq{}

semantics for Pi:
\PIMEMstate{}
\PIMEMstep{}

>>>>

\title{Fractional Types}
\subtitle{Expressive and Safe Space Management for Ancilla Bits}
\author{Chao-Hong Chen}
\affiliation{
  \institution{Indiana University}
}

@@

There are two main reasons we are calling the new type constructor a
\emph{fractional type} and using the suggestive notation
$\oneover{t}$:
\begin{itemize}
\item Categorical: ... explain and point to section with examples
  showing 1/ab = 1/a  1/b etc.
\item Operational ... this section; bits = log of size; fractional
  needs negative bits; i.e. space collector; make this precise  
\end{itemize}

%% cardinality of pi type:
%% \PIMEMcard{}
%%   
%% enumeration:
%% \PIMEMenum{}
%% 
%%  combinator preserve size:
%% \PIMEMcardeq{}
%% 
%%  semantics for Pi:
%% \PIMEMstate{}
%% \PIMEMstep{}
